FinalManuscript_DISCS_UG

### 2019-01-19 pcsc-paper/parts/02_01_paillier.tex
Fixed typo in FP extension
Fixed in both pcsc paper and thesis manuscript
Minor fixes

\subsubsection{Key Generation}
We first define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}(p-1,q-1)$.
Then we select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$.
We denote the public key as $(g,n)$ and the private key $(p,q)$.
\subsubsection{Encryption and Decryption}
The encryption function to encrypt a plaintext $m \in \mathbb{Z}_n$ given a public key $(g,n)$ is defined as
\begin{align*}
	E(m) = g^m \cdot r^n \mod{n^2},
\end{align*}
where $r$ is a random non-negative integer less than $n^2$.
The decryption function to decrypt a ciphertext $c \in \mathbb{Z}^*_{n^2}$ given a private key $(p,q)$ is defined as:
\begin{align*}
	D(c) = L\left(c^\lambda \bmod n^2\right) \cdot \left(L\left(g^\lambda \bmod n^2\right)\right)^{-1} \mod n.
\end{align*}
\subsubsection{Homomorphic Properties of the Paillier Cryptosystem}
The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively. They are defined as follows.

For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold:
\begin{align*}
	D(E(m_1)g^k\bmod n^2)=(m_1+k)\bmod n,\\
	D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n,\\
	D(E(m_1)^k\bmod n^2)= km_1\bmod n.
\end{align*}

\subsection{Floating-Point Arithmetic}
\label{sec:fp_operations}
The Paillier cryptosystem encrypts and allows operations on integers. We now describe several extensions to the Paillier cryptosystem discussed in the literature which allow us to perform privacy-preserving floating-point arithmetic.

@@

We represent a floating-point (FP) number as a pair of two integers $(m,e)$ representing the mantissa and exponent of the FP number with respect to a base $b$. The mantissa $m$ is encrypted, while the exponent $e$ is unencrypted.
Let $a,b,c$ be FP numbers represented by the pairs $(m_a,e_a),(m_b,e_b),(m_c,e_c)$ respectively. Let $\oplus,\otimes$ represent the homomorphic operations which correspond to the addition and multiplication of integers in the Paillier cryptosystem, respectively. We define the corresponding FP number operations as follows:
\begin{description}
  \item[Addition.]
    To compute $E(c)=E(a+b)$ we compute
    \begin{align*}
      E(m_c) &= E(m_1) \oplus (b^{e_b-e_a} \otimes E(m_b)), e_c = e_a & \text{ if } e_a \leq e_b, \\
      E(m_c) &= E(m_b) \oplus (b^{e_a-e_b} \otimes E(m_a)), e_c = e_b & \text{ if } e_a > e_b.
    \end{align*}
  \item[Scalar multiplication.]
    To compute $E(c) = E(ab)$, where $a$ and $E(b)$ are known (i.e. $m_a$ is not encrypted), we compute
    \begin{align*}
      E(m_c) &= m_a \otimes E(m_b),\\
      e_c &= e_a + e_b.
    \end{align*}
\end{description}
\subsubsection{Secure Division}
We can use the following two-party scheme defined in~\cite{boukoros_lightweight_2017} to perform privacy-preserving division.

Suppose Bob has $E(x)$ and $E(y)$ and wants to obtain $E(x/y)$ without exposing the value of either variable.
\begin{itemize}
	\item Bob first selects a random non-zero number $r$ and computes $E(rx)$ and $E(ry)$. Bob can do this since $r$ is a plaintext constant.
	\item Bob sends $E(rx)$ and $E(ry)$ to Alice, who decrypts both values and computes $x/y$ in the plaintext domain.
	\item Alice encrypts and sends $E(x/y)$ to Bob.
\end{itemize}

@@

Suppose Alice encrypts an integer $x$ and sends it so Bob has $E(x)$, and wants to obtain $E(x^2)$ without exposing the value of $x$.
\begin{itemize}
	\item Bob first selects a random integer $r$ and computes $E(x+r)$. Bob can do this since $r$ is a plaintext constant.
	\item Bob sends $E(x+r)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
	\item Alice squares $x+r$ and encrypts the result. She sends $E((x+r)^2)$ to Bob.
	\item Bob computes $E(-2rx + r^2)$. He then computes
	\begin{align*}
		E((x+r)^2)E(-2rx + r^2) = E(x^2).
	\end{align*}
\end{itemize}

\subsubsection{Secure Multiplication}
We can use the secure squaring protocol to arrive at a secure multiplication protocol, which then allows for the evaluation of polynomials.
Suppose Alice encrypts integers $x$ and $y$, and Bob has $E(x), E(y)$ and wants to obtain $E(xy)$.
\begin{itemize}
	\item Bob acquires $E(x^2)$ and $E(y^2)$ using the secure squaring protocol.
	\item Bob sends $E(x+y)$ to Alice, who decrypts the ciphertext to obtain $x+y$.
	\item Alice sends $E((x+y)^2)$ to Bob.
	\item Bob then computes
	\begin{align*}
		\frac{1}{2}E((x+y)^2)E(x^2)^{-1}E(y^2)^{-1} &= \frac{1}{2}E((x+y)^2 - x^2 - y^2)\\
		&= \frac{1}{2}E(2xy)\\
		&= E(xy).
	\end{align*}
\end{itemize}

>>>>

\subsubsection{Key Generation}
We first define a function $L\left(x\right)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}\left(p-1,q-1\right)$.
Then we select an integer $g$ such that $\gcd\left(L\left(g^\lambda \bmod n^2\right), n\right) = 1$ and $0\leq g \leq n^2$.
We denote the public key as $(g,n)$ and the private key $(p,q)$.
\subsubsection{Encryption and Decryption}
The encryption function to encrypt a plaintext $m \in \mathbb{Z}_n$ given a public key $(g,n)$ is defined as
\begin{equation*}
	E\left(m\right) = g^m \cdot r^n \mod{n^2},
\end{equation*}
where $r$ is a random non-negative integer less than $n^2$.
The decryption function to decrypt a ciphertext $c \in \mathbb{Z}^*_{n^2}$ given a private key $(p,q)$ is defined as:
\begin{equation*}
	D\left(c\right) = L\left(c^\lambda \bmod n^2\right) \cdot \left(L\left(g^\lambda \bmod n^2\right)\right)^{-1} \mod n.
\end{equation*}
\subsubsection{Homomorphic Properties of the Paillier Cryptosystem}
The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively. They are defined as follows.

For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold:
\begin{align*}
	D\left(E\left(m_1\right) g^k\bmod n^2\right) &= \left(m_1+k\right)\bmod n,\\
	D\left(E\left(m_1\right) E\left(m_2\right)\bmod n^2\right) &= \left(m_1+m_2\right)\bmod n,\\
	D\left(E\left(m_1\right)^k\bmod n^2\right) &= km_1\bmod n.
\end{align*}

\subsection{Floating-Point Arithmetic}
\label{sec:fp_arithmetic}
The Paillier cryptosystem encrypts and allows operations on integers. We now describe several extensions to the Paillier cryptosystem discussed in the literature which allow us to perform privacy-preserving floating-point arithmetic.

@@

We represent a floating-point (FP) number as a pair of two integers $(m,e)$ representing the mantissa and exponent of the FP number with respect to a base $b$. The mantissa $m$ is encrypted, while the exponent $e$ is unencrypted.
Let $a,b,c$ be FP numbers represented by the pairs $(m_a,e_a),(m_b,e_b),(m_c,e_c)$ respectively. Let $\oplus,\otimes$ represent the homomorphic operations which correspond to the addition and multiplication of integers in the Paillier cryptosystem, respectively. We define the corresponding FP number operations as follows:
\begin{description}
  \item[Addition.]
    To compute $E\left(c\right)=E\left(a+b\right)$ we compute
    \begin{align*}
		E\left(m_c\right) &= E\left(m_a\right) \oplus \left(b^{e_b-e_a} \otimes E\left(m_b\right)\right) \text{and } e_c = e_a & \text{ if } e_a \leq e_b, \\
		E\left(m_c\right) &= E\left(m_b\right) \oplus \left(b^{e_a-e_b} \otimes E\left(m_a\right)\right) \text{and } e_c = e_b & \text{ if } e_a > e_b.
	\end{align*}
	% \begin{align*}
	% 	E\left(m_c\right) &= 
	% 	\begin{cases}
	% 		E\left(m_a\right) \oplus \left(b^{e_b-e_a} \otimes E\left(m_b\right)\right) & \text{if } e_a \leq e_b \\
	% 		E\left(m_b\right) \oplus \left(b^{e_a-e_b} \otimes E\left(m_a\right)\right) & \text{if } e_a > e_b
	% 	\end{cases} \\
	% 	% \text{ and }
	% 	e_c &= \min\left(e_a, e_b \right).	
	% 	% \begin{cases}
	% 	% 	e_a & \text{if } e_a \leq e_b \\
	% 	% 	e_b & \text{if } e_a > e_b
	% 	% \end{cases}.
	% \end{align*}
  \item[Scalar multiplication.]
    To compute $E\left(c\right) = E\left(ab\right)$, where $a$ and $E\left(b\right)$ are known (i.e., $m_a$ is not encrypted), we compute
    \begin{align*}
      E\left(m_c\right) &= m_a \otimes E\left(m_b\right),\\
      e_c &= e_a + e_b.
    \end{align*}
\end{description}

\subsubsection{Secure Division}
We can use the following two-party scheme defined in~\cite{boukoros_lightweight_2017} to perform privacy-preserving division.

Suppose Bob has $E\left(x\right)$ and $E\left(y\right)$ and wants to obtain $E\left(x/y\right)$ without exposing the value of either variable.
\begin{itemize}
	\item Bob first selects a random non-zero number $r$ and computes $E\left(rx\right)$ and $E\left(ry\right)$. Bob can do this since $r$ is a plaintext constant.
	\item Bob sends $E\left(rx\right)$ and $E\left(ry\right)$ to Alice, who decrypts both values and computes $x/y$ in the plaintext domain.
	\item Alice encrypts and sends $E\left(x/y\right)$ to Bob.
\end{itemize}

@@

Suppose Alice encrypts an integer $x$ and sends it so Bob has $E\left(x\right)$, and wants to obtain $E\left(x^2\right)$ without exposing the value of $x$.
\begin{itemize}
	\item Bob first selects a random integer $r$ and computes $E\left(x+r\right)$. Bob can do this since $r$ is a plaintext constant.
	\item Bob sends $E\left(x+r\right)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
	\item Alice squares $x+r$ and encrypts the result. She sends $E\left(\left(x+r\right)^2\right)$ to Bob.
	\item Bob computes $E\left(-2rx + r^2\right)$. He then computes
	\begin{align*}
		E\left(\left(x+r\right)^2\right)E\left(-2rx + r^2\right) = E\left(x^2\right).
	\end{align*}
\end{itemize}

\subsubsection{Secure Multiplication}
We can use the secure squaring protocol to arrive at a secure multiplication protocol, which then allows for the evaluation of polynomials.
Suppose Alice encrypts integers $x$ and $y$, and Bob has $E\left(x\right), E\left(y\right)$ and wants to obtain $E\left(xy\right)$.
\begin{itemize}
	\item Bob acquires $E\left(x^2\right)$ and $E\left(y^2\right)$ using the secure squaring protocol.
	\item Bob sends $E\left(x+y\right)$ to Alice, who decrypts the ciphertext to obtain $x+y$.
	\item Alice sends $E\left(\left(x+y\right)^2\right)$ to Bob.
	\item Bob then computes
	\begin{align*}
		\frac{1}{2}E\left(\left(x+y\right)^2\right)E\left(x^2\right)^{-1}E\left(y^2\right)^{-1} &= \frac{1}{2}E\left(\left(x+y\right)^2 - x^2 - y^2\right)\\
		&= \frac{1}{2}E\left(2xy\right)\\
		&= E\left(xy\right).
	\end{align*}
\end{itemize}

### 2019-01-19 pcsc-paper/parts/03_exponentialandlogarithmic.tex
Periods and commas everywhere
added periods to equations
also some minor wording changes
Minor fixes

Since the approximation by Khattri is accurate for values of $x$ near zero, we can scale the approximation by a constant factor $\alpha$ by expressing $\log(1+x)$ as follows, similarly using the substitution $x=1/n$:
\begin{align*}
	\log{(1+x)} &= \log{\left(\frac{\alpha + \alpha x}{\alpha}\right)}\\
	&= \log{(\alpha + \alpha x)} - \log{\alpha}\\
	&= \log{\left(\alpha+\frac{\alpha}{n}\right)} - \log{\alpha}\\
	&= \log{\left(\frac{\alpha n + \alpha}{n}\right)} - \log{\alpha}\\
	&= \int_{n}^{\alpha n + \alpha}{\frac{1}{t}\diff t} - \log{\alpha}.
\end{align*}

Applying the five-point Gauss--Legendre quadrature rule to approximate $\int_{n}^{\alpha n + \alpha}{\frac{1}{x}\diff x}$ with $\alpha = 1/16$ using SageMath 8.3, we arrive at the approximation:
\begin{align}\label{eq:optimal_log_approximation}
	\begin{split}
		&\log(1+x) \\
		&\approx \frac{137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 - 121239315x - 257804775}
		{30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x + 3122577)}\\
		&+ \log{16}
	\end{split}
\end{align}

We note that the approximation in Equation~\ref{eq:optimal_log_approximation} requires the value of $\log{16}$. This can be computed in the plaintext domain and added to an encrypted value using the properties of the Paillier cryptosystem. The remaining arithmetic operations in the approximation can be computed in the encrypted domain, using the protocols described in Section~\ref{sec:fp_operations}. Therefore, this approximation can be calculated in a privacy-preserving manner.

@@

We now show how we used numerical methods to determine that a scaling factor of $\alpha = 1/16$ minimizes the maximum absolute error of the scaled approximation for $\log{(1+x)}$, within the range $x \in [0, 255]$.
Let $I(x,\alpha)$ be the function obtained by approximating $\int_{n}^{\alpha n + \alpha}{\frac{1}{x}\diff x}$ with five-point Gauss--Legendre quadrature. The absolute error of the approximation compared to  $\log{(1+x)}$ at a given $x$ and $\alpha$ is given by the following function.
\begin{align*}
	A(x,\alpha) = \left| I(x,\alpha) - \log\alpha - \log{(1+x)}\right|.
\end{align*}

We want to show that the function
\begin{align*}
	f(\alpha) = \max_{0\leq x \leq 255}{A(x,\alpha)}
\end{align*}
is minimized at $\alpha = 1/16$.
We consider the functions $A(0,\alpha)$ and $A(255,\alpha)$. These are plotted in Figure~\ref{fig:endpoint_plot}.

It can be determined numerically using SageMath 8.3 that a local minimum of $\max(A(0,\alpha),A(255,\alpha))$ on the interval $[0,1]$ is at $\alpha = 1/16$, which is found at the intersection of the two graphs.
\begin{figure}[!ht]
	\centering
    \begin{tikzpicture}
		\begin{semilogyaxis}[
			% height=6cm, width=9cm,
			xmin=0, xmax=1,
			ymin=5e-7, ymax=1.3,
			xlabel={$\alpha$}, ylabel={Absolute error},
			grid=major,
			extra x ticks={1/16},
			extra x tick labels={$\frac{1}{16}$},
			legend pos=south east,
			legend cell align=left,
			tick scale binop=\times,
		]
		% \addplot[thick, ACMDarkBlue, domain=0:1, samples=200]{1/30*abs((137*x^5 + 1625*x^4 + 2000*x^3 - 2000*x^2 - 30*(x^5 + 25*x^4 + 100*x^3 + 100*x^2 + 25*x + 1)*ln(x) - 1625*x - 137)/(x^5 + 25*x^4 + 100*x^3 + 100*x^2 + 25*x + 1))};
		% \addplot[thick, ACMOrange, domain=0:1, samples=200]{abs(-1/30*(32346117281250*x^5*ln(x) - 150633093005312*x^5 - 6979321856000*x^4 - 33554432000*x^3 + 131072000*x^2 + 30*(x^5 + 25*x^4 + 100*x^3 + 100*x^2 + 25*x + 1)*ln(x) + 38250*(x^5 + 20*x^4 + 60*x^3 + 40*x^2 + 5*x)*ln(x) + 19507500*(x^5 + 15*x^4 + 30*x^3 + 10*x^2)*ln(x) + 4974412500*(x^5 + 10*x^4 + 10*x^3)*ln(x) + 634237593750*(x^5 + 5*x^4)*ln(x) + 416000*x + 137)/(1099511627776*x^5 + 107374182400*x^4 + 1677721600*x^3 + 6553600*x^2 + 6400*x + 1) - 8*ln(2))};
		\addplot[thick, ACMDarkBlue, domain=0:1] table[x=alpha, y=x0] {plots/abs_err_sl_0_255.txt};
		\addplot[thick, ACMOrange, domain=0:1] table[x=alpha, y=x255] {plots/abs_err_sl_0_255.txt};
		\legend{$x=0$, $x=255$}
	\end{semilogyaxis}
	\end{tikzpicture}%
	\caption{Graphs of $A(x,\alpha)$ at $x=0$ and $x=255$}
	\label{fig:endpoint_plot}
\end{figure}
We then consider the function $A(x,1/16)$, shown in Figure~\ref{fig:single_alpha_plot}.
It was determined numerically that the local maxima of $A(x,1/16)$ on the interval occur at $x=0$ and $x=255$. Since a scaling factor other than $\alpha=1/16$ yields a higher absolute error at either $x=0$ or $x=255$, as seen in Figure~\ref{fig:endpoint_plot}, it follows that a scaling factor of $\alpha = 1/16$ minimizes the maximum absolute error of the scaled approximation for $\log{(1+x)}$, within the range $x \in [0, 255]$.
\begin{figure}[ht]
	\centering
	\begin{tikzpicture}
		\begin{semilogyaxis}[
			xmin=0, xmax=300,
			ymin=1e-15, ymax=0.035,
			xlabel={$x$}, ylabel={Absolute error},
			grid=major,
			legend pos=south east,
			legend cell align=left,
			tick scale binop=\times,
		]
		% \addplot[very thick, domain=0:300, samples=300]{abs(1/30*(137*x^5 + 26685*x^4 + 617370*x^3 - 6498630*x^2 - 121239315*x - 257804775)/(x^5 + 405*x^4 + 27210*x^3 + 488810*x^2 + 2536005*x + 3122577) - ln(1/16) - ln(x + 1))};
		\addplot[thick, ACMDarkBlue] table[x=x, y=error] {plots/abs_err_scaledlog.txt};
	\end{semilogyaxis}
	\end{tikzpicture}%
	\caption{Graph of $A(x,1/16)$, the absolute error of the approximation in Equation~\ref{eq:optimal_log_approximation} given a scaling factor of $\alpha=1/16$}
	\label{fig:single_alpha_plot}
\end{figure}

@@

As a concrete example, evaluating partial sums of the series representation for the exponential function
\begin{align*}
	e^x = \sum_{n=0}^{\infty}{\frac{x^n}{n!}}
\end{align*}
is a valid approach for privacy-preserving computation, as this series converges for all $x$.

>>>>

Since the approximation by Khattri is accurate for values of $x$ near zero, we can scale the approximation by a constant factor $\alpha$ by expressing $\log(1+x)$ as follows, similarly using the substitution $x=1/n$:
\begin{align*}
	\log{\left(1+x\right)} &= \log{\left(\frac{\alpha + \alpha x}{\alpha}\right)}\\
	&= \log{(\alpha + \alpha x)} - \log{\alpha}\\
	&= \log{\left(\alpha+\frac{\alpha}{n}\right)} - \log{\alpha}\\
	&= \log{\left(\frac{\alpha n + \alpha}{n}\right)} - \log{\alpha}\\
	&= \int_{n}^{\alpha n + \alpha}{\frac{1}{t}\diff t} - \log{\alpha}.
\end{align*}

Applying the five-point Gauss--Legendre quadrature rule to approximate $\int_{n}^{\alpha n + \alpha}{\frac{1}{x}\diff x}$ with $\alpha = 1/16$ using SageMath 8.3, we arrive at the approximation:
\begin{align}\label{eq:optimal_log_approximation}
	\begin{split}
		&\log\left(1+x\right) \\
		&\approx \frac{137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 - 121239315x - 257804775}
		{30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x + 3122577)}\\
		&+ \log{16}.
	\end{split}
\end{align}

We note that the approximation in Equation~\ref{eq:optimal_log_approximation} requires the value of $\log{16}$. This can be computed in the plaintext domain and added to an encrypted value using the properties of the Paillier cryptosystem. The remaining arithmetic operations in the approximation can be computed in the encrypted domain, using the protocols described in Section~\ref{sec:fp_arithmetic}. Therefore, this approximation can be calculated in a privacy-preserving manner.

@@

We now show how we used numerical methods to determine that a scaling factor of $\alpha = 1/16$ minimizes the maximum absolute error of the scaled approximation for $\log{\left(1+x\right)}$, within the range $x \in [0, 255]$.

Let $I\left(x,\alpha\right)$ be the function obtained by approximating $\int_{n}^{\alpha n + \alpha}{\frac{1}{x}\diff x}$ with five-point Gauss--Legendre quadrature. The absolute error of the approximation compared to $\log{\left(1+x\right)}$ at a given $x$ and $\alpha$ is given by the following function.
\begin{align*}
	A\left(x,\alpha\right) = \left| I\left(x,\alpha\right) - \log\alpha - \log{\left(1+x\right)}\right|.
\end{align*}
We want to show that the function
\begin{align*}
	f\left(\alpha\right) = \max_{0\leq x \leq 255}{A\left(x,\alpha\right)}
\end{align*}
is minimized at $\alpha = 1/16$.
We consider the functions $A\left(0,\alpha\right)$ and $A\left(255,\alpha\right)$. These are plotted in Figure~\ref{fig:endpoint_plot}.
\begin{figure}[!ht]
	\centering
    \begin{tikzpicture}
		\begin{semilogyaxis}[
			% height=6cm, width=9cm,
			xmin=0, xmax=1,
			ymin=5e-7, ymax=1.3,
			xlabel={$\alpha$}, ylabel={Absolute error},
			grid=major,
			extra x ticks={1/16},
			extra x tick labels={$\frac{1}{16}$},
			legend pos=south east,
			legend cell align=left,
			tick scale binop=\times,
		]
		\addplot[thick, ACMDarkBlue, domain=0:1] table[x=alpha, y=x0] {plots/abs_err_sl_0_255.txt};
		\addplot[thick, ACMOrange, domain=0:1] table[x=alpha, y=x255] {plots/abs_err_sl_0_255.txt};
		\legend{$x=0$, $x=255$}
		% \legend{$A\left(0,\alpha \right)$, $A\left(255,\alpha \right)$}
	\end{semilogyaxis}
	\end{tikzpicture}%
	\caption{Graphs of $A\left(x,\alpha\right)$ at $x=0$ and $x=255$}
	\label{fig:endpoint_plot}
\end{figure}

It can be determined numerically using SageMath 8.3 that a local minimum of $\max\left(A\left(0,\alpha\right),A\left(255,\alpha\right)\right)$ on the interval $[0,1]$ is at $\alpha = 1/16$, which is found at the intersection of the two graphs.

We then consider the function $A\left(x,1/16\right)$, shown in Figure~\ref{fig:single_alpha_plot}.
It was determined numerically that the local maxima of $A\left(x,1/16\right)$ on the interval occur at $x=0$ and $x=255$. Since a scaling factor other than $\alpha=1/16$ yields a higher absolute error at either $x=0$ or $x=255$, as seen in Figure~\ref{fig:endpoint_plot}, it follows that a scaling factor of $\alpha = 1/16$ minimizes the maximum absolute error of the scaled approximation for $\log{\left(1+x\right)}$, within the range $x \in [0, 255]$.
\begin{figure}[ht]
	\centering
	\begin{tikzpicture}
		\begin{semilogyaxis}[
			xmin=0, xmax=300,
			ymin=1e-15, ymax=0.035,
			xlabel={$x$}, ylabel={Absolute error},
			grid=major,
			legend pos=south east,
			legend cell align=left,
			tick scale binop=\times,
		]
		% \addplot[very thick, domain=0:300, samples=300]{abs(1/30*(137*x^5 + 26685*x^4 + 617370*x^3 - 6498630*x^2 - 121239315*x - 257804775)/(x^5 + 405*x^4 + 27210*x^3 + 488810*x^2 + 2536005*x + 3122577) - ln(1/16) - ln(x + 1))};
		\addplot[thick, ACMDarkBlue] table[x=x, y=error] {plots/abs_err_scaledlog.txt};
	\end{semilogyaxis}
	\end{tikzpicture}%
	\caption{Graph of $A\left(x,1/16\right)$, the absolute error of the approximation in Equation~\ref{eq:optimal_log_approximation} given a scaling factor of $\alpha=1/16$}
	\label{fig:single_alpha_plot}
\end{figure}

@@

As a concrete example, evaluating partial sums of the series representation for the exponential function,
\begin{align*}
	e^x = \sum_{n=0}^{\infty}{\frac{x^n}{n!}},
\end{align*}
is a valid approach for privacy-preserving computation, as this series converges for all $x$.

### 2019-01-19 pcsc-paper/parts/05_testsforaccuracy.tex
Minor fixes

\section{Experiments on Accuracy}
We implemented privacy-preserving floating-point arithmetic using the system described in Section~\ref{sec:fp_operations}, through the \texttt{python-paillier} library (\url{https://github.com/n1analytics/python-paillier}) running on Python~3.6.5.

\subsection{Logarithm Approximation}
We then computed $\log(1+x)$ for various encrypted inputs using both the original quadrature formula by Khattri (Equation~\ref{eq:standard_logarithm_quadrature}) and our scaled approximation (Equation~\ref{eq:optimal_log_approximation}). These were compared with the values returned by the built-in logarithm function in Python. Several data points are shown in Table~\ref{tab:log_approximation}.

We note that the privacy-preserving floating-point arithmetic resulted in some degree of floating-point error, as the observed floating point error in Table~\ref{tab:log_approximation} is greater than the raw absolute error observed in Figure~\ref{fig:log_error_comparison}. However, it can still be seen that the error of the scaled approximation is less than that of the original approximation for large inputs, although this approximation loses accuracy for smaller inputs.
\begin{table}[h]
	\caption{Comparison of logarithm approximation errors under Paillier}
	\label{tab:log_approximation}
	\begin{tabular}{lcc}
		\toprule
		Input & Original quadrature & Scaled quadrature\\
		\midrule
		$\log 1$ & $0$ & $2.053729 \times 10^{-2}$\\
		$\log 10$ & $2.833179 \times 10^{-2} $ & $2.280124 \times 10^{-1}$\\
		$\log 50$ & $2.170779 \times 10^{-2}$ & $2.437148 \times 10^{-2}$\\
		$\log 100$ & $3.524916 \times 10^{-1}$ & $2.122159 \times 10^{-2}$\\
		$\log 200$ & $8.859869 \times 10^{-1}$ & $1.441611 \times 10^{-1}$\\
		$\log 256$ & $1.098463 \times 10^{0}$ & $1.993136 \times 10^{-1}$\\
	\bottomrule
\end{tabular}
\end{table}

@@

\begin{table}[h]
	\caption{Comparison of inverse tangent approximation errors under Paillier}
	\label{tab:arctan_approximation}
	\begin{tabular}{lcc}
		\toprule
		Input & Partial sum of infinite series & Quadrature\\
		\midrule
		$\arctan -1$ & $6.564089 \times 10^{-1}$ & $4.629557 \times 10^{-1}$\\
		$\arctan -0.1$ & $4.523405 \times 10^{-3}$ & $1.451929 \times 10^{-3}$\\
		$\arctan -0.01$ & $4.665260 \times 10^{-6}$ & $1.472027 \times 10^{-6}$\\
		$\arctan 0$ & $0$ & $0$\\
		$\arctan 0.01$ & $4.665228 \times 10^{-6}$ & $1.472020 \times 10^{-6}$\\
		$\arctan 0.1$ & $4.523405 \times 10^{-3} $ & $1.451929 \times 10^{-3}$\\
		$\arctan 1$ & $6.564089 \times 10^{-1} $ & $4.629557 \times 10^{-1}$\\
	\bottomrule
\end{tabular}
\end{table}

>>>>

\section{Experiments on Accuracy}
We implemented privacy-preserving floating-point arithmetic using the system described in Section~\ref{sec:fp_arithmetic}, through the \texttt{python-paillier} library (\url{https://github.com/n1analytics/python-paillier}) running on Python~3.6.5.

\subsection{Logarithm Approximation}
We then computed $\log\left(1+x\right)$ for various encrypted inputs using both the original quadrature formula by Khattri (Equation~\ref{eq:standard_logarithm_quadrature}) and our scaled approximation (Equation~\ref{eq:optimal_log_approximation}). These were compared with the values returned by the built-in logarithm function in Python. Several data points are shown in Table~\ref{tab:log_approximation}.

We note that the privacy-preserving floating-point arithmetic resulted in some degree of floating-point error, as the observed floating point error in Table~\ref{tab:log_approximation} is greater than the raw absolute error observed in Figure~\ref{fig:log_error_comparison}. However, it can still be seen that the error of the scaled approximation is less than that of the original approximation for large inputs, although this approximation loses accuracy for smaller inputs.
\begin{table}[ht]
	\caption{Comparison of logarithm approximation errors under Paillier}
	\label{tab:log_approximation}
	\begin{tabular}{lcc}
		\toprule
		Input & Original quadrature & Scaled quadrature\\
		\midrule
		$\log 1$ & $0$ & $2.053729 \times 10^{-2}$\\
		$\log 10$ & $2.833179 \times 10^{-2} $ & $2.280124 \times 10^{-1}$\\
		$\log 50$ & $2.170779 \times 10^{-2}$ & $2.437148 \times 10^{-2}$\\
		$\log 100$ & $3.524916 \times 10^{-1}$ & $2.122159 \times 10^{-2}$\\
		$\log 200$ & $8.859869 \times 10^{-1}$ & $1.441611 \times 10^{-1}$\\
		$\log 256$ & $1.098463 \times 10^{0}$ & $1.993136 \times 10^{-1}$\\
	\bottomrule
\end{tabular}
\end{table}

@@

\begin{table}[ht]
	\caption{Comparison of inverse tangent approximation errors under Paillier}
	\label{tab:arctan_approximation}
	\begin{tabular}{lcc}
		\toprule
		Input & Partial sum of infinite series & Quadrature\\
		\midrule
		$\arctan -1$ & $6.564089 \times 10^{-1}$ & $4.629557 \times 10^{-1}$\\
		$\arctan -0.1$ & $4.523405 \times 10^{-3}$ & $1.451929 \times 10^{-3}$\\
		$\arctan -0.01$ & $4.665260 \times 10^{-6}$ & $1.472027 \times 10^{-6}$\\
		$\arctan 0$ & $0$ & $0$\\
		$\arctan 0.01$ & $4.665228 \times 10^{-6}$ & $1.472020 \times 10^{-6}$\\
		$\arctan 0.1$ & $4.523405 \times 10^{-3} $ & $1.451929 \times 10^{-3}$\\
		$\arctan 1$ & $6.564089 \times 10^{-1} $ & $4.629557 \times 10^{-1}$\\
	\bottomrule
\end{tabular}
\end{table}
